---
title: "Presentation title"
author: "Author name"
format:
  revealjs: 
    theme: simple
    incremental: true
    slide-number: true
    chalkboard: 
      buttons: true
    preview-links: auto
    css: styles.css
---

# Overview

Check the [Quarto website](https://quarto.org/docs/) to see a complete demo of Quarto presentation features.


## Preview Links

Navigate to hyperlinks without disrupting the flow of your presentation.

Use the `preview-links` option to open links in an iframe on top of your slides. Try clicking the link below for a demonstration:

::: {style="text-align: center; margin-top: 1em"}
[https://quarto.org/docs/presentations/revealjs/](https://quarto.org/docs/presentations/revealjs/){preview-link="true" style="text-align: center"}
:::

::: footer
Learn more: [Preview Links](https://quarto.org/docs/presentations/revealjs/presenting.html#preview-links)
:::

# Running R Code

## Simple R Examples

Here are some basic R operations you can run:

```{r}
#| echo: true
#| eval: true

# Basic arithmetic
x <- 5 + 3
print(x)

# Create a vector
numbers <- c(1, 2, 3, 4, 5)
print(numbers)

# Calculate mean
mean_value <- mean(numbers)
print(paste("Mean:", mean_value))
```

## Data Visualization

```{r}
#| echo: true
#| eval: true
#| fig-height: 4

library(ggplot2)

# Simple scatter plot
data <- data.frame(
  x = 1:10,
  y = (1:10)^2 + rnorm(10, 0, 5)
)

ggplot(data, aes(x = x, y = y)) +
  geom_point(size = 3, color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Simple Scatter Plot", x = "X values", y = "Y values") +
  theme_minimal()
```
