---
title: "Presentation title"
author: "Author name"
format:
  revealjs: 
    theme: simple
    incremental: true
    slide-number: true
    chalkboard: 
      buttons: true
    preview-links: auto
    css: styles.css
---

# Overview

Check the [Quarto website](https://quarto.org/docs/) to see a complete demo of Quarto presentation features.


## Preview Links

Navigate to hyperlinks without disrupting the flow of your presentation.

Use the `preview-links` option to open links in an iframe on top of your slides. Try clicking the link below for a demonstration:

::: {style="text-align: center; margin-top: 1em"}
[https://quarto.org/docs/presentations/revealjs/](https://quarto.org/docs/presentations/revealjs/){preview-link="true" style="text-align: center"}
:::

::: footer
Learn more: [Preview Links](https://quarto.org/docs/presentations/revealjs/presenting.html#preview-links)
:::

# Running R Code

## Simple R Examples

Here are some basic R operations you can run:

```{r}
#| echo: true
#| eval: true

# Basic arithmetic
x <- 5 + 3
print(x)

# Create a vector
numbers <- c(1, 2, 3, 4, 5)
print(numbers)

# Calculate mean
mean_value <- mean(numbers)
print(paste("Mean:", mean_value))
```

## Basic Plotting

```{r}
#| echo: true
#| eval: true
#| fig-height: 4

# Simple plot using base R
x <- 1:10
y <- x^2

plot(x, y,
     type = "b",
     col = "blue",
     pch = 16,
     main = "Simple Plot with Base R",
     xlab = "X values",
     ylab = "Y values")
```
